Modeling the impacts of park access on health outcomes: a utility-based accessibility approach

### 2020-09-24 manuscript/manuscript.tex
Build document with revisions

In spite of its flexibility and basis in choice theory, utility-based
accessibility measures have not received much application in the
accessibility literature compared with distance-based or even
gravity-based measures. \citet{Vale2016} present a descriptive
classification of active accessibility techniques, and explicitly
dismiss utility-based metrics for incorporating randomness. The
accessibility formula presented in Equation \ref{eq:utility} is the
expectation of a random utility process, and is not in and of itself
random any more than the gravity model is random. Utility-based
accessibility metrics are commonly used, however, in alternatives
analyses of transit infrastructure improvements \citep{DeJong2007}. A
reason for this is likely that a regional travel demand model is
available to the analysts, thus making calibrated and multimodal logsums
readily available \citep{Geurs2010}.

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.318e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
that the coefficients are equivalent, as the differences are at no point
practically different from each other. The consequences of rejecting the
null hypothesis in this case would be to suggest a model with spatial
dependence of the dependent variable; as stated above, we feel that such
a relationship is unreasonable. As a consequence of these analyses, we
adopt the SDEM specification moving forward as the spatial lag of the
errors is significant and the overall log likelihood of the SDEM is
higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Tue Sep 22 16:54:49 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

\midrule
Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
\bottomrule
\end{tabular}
\end{table*}

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and
accessibility coefficients for three models using different
specifications of the utility equation, as well as the ten-minute walk
buffer calculated by ParkScore. Note that the model called ``Size and
Distance'' is precisely the model labeled ``SDEM'' in Table
\ref{tab:slx-sdem}. The controlling covariates are suppressed for
clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels}
of the Supplementary Material. Each of the three utility-based
specifications is significant at the \(\alpha = 0.05\) level or lower,
and is of the hypothesized directionality. That is, residents living in
tracts with increased utility-based accessibility to green spaces show a
significantly higher physical activity participation rate. Taking the
rough mean of the 2 estimated utility-based coefficients, moving from
the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
(\(A_i = 3\)) is expected to raise the physical activity rate by 0.9
percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor
park access is anywhere between 0.06 and 1.8 percentage points.

The 10-minute walk buffer is considerably less useful at isolating the
effects of park ``access'' on physical activity rates. As so few tracts
are located outside of the buffer, the standard error of the estimated
effect is large and implies an effect on activity rates anywhere from a
loss of 1.08 percentage points to a gain of 8.1.

@@

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the
destination parks as well as the people who might use them. As an
illustration: the park-going population could be separated into at least
four delineated clusters, each preferring different amenities of a park:

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. In this paper, we proceed only
incrementally towards this by adding some selected park amenities as an
element of each park's attractiveness above and beyond its size. The set
of amenities we included in the utility calculation --- and the
contribution of each amenity to the overall utility --- was dictated by
the availability of data on the park amenities in New York City and our
ability to find comparable prior studies with transferrable utility
parameters. We can envision a study where mobile device data revealing
the home locations of park users would be paired with more detailed park
amenities and use data (e.g.~geolocated Twitter data \emph{a la}
\citet{roberts2017using}) to estimate the utility contribution of these
features. This could in turn provide a more nuanced understanding of the
relationship between park accessibility, use, and health outcomes.

@@

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted.

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park accessibility and these metrics, previous
literature has produced mixed findings, perhaps owing to the range of
variables modeled and the coarse spatial scale of the analyses. Using
New York City as a case study, we presented a holistic and flexible
measurement for park accessibility that compares the continuous distance
to all parks in the region, weighted against the size of the park and
its other amenities, with weights determinable through revealed
preferences. In terms of physical activity, we found a positive
relationship where the least park-accessible tracts have an expected
physical activity participation rate between 0.06 and 1.8 percentage
points lower than the most accessible tracts. We also found a suggestive
though not significant relationship between park accessibility and
expected obesity rates \emph{in addition to} the effect of physical
activity participation.

In both cases a common, isochrone-based analysis estimated a
statistically weak relationship with greater uncertainty. Isochrone
analyses are relatively common in the literature, perhaps because of the
widespread availability of and training in GIS software. In spite of
their widespread use, isochrones are relatively limited in terms of both
their theoretical underpinnings and their flexibility to accommodate
attributes of parks beyond their proximity. And even proximity may not
be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends a
more comprehensive and flexible approach for measuring the impact of
park access on health outcomes. Adopting utility-based accessibilities
of the kind used in this study will allow researchers to encompass the
full range of park amenities in their accessibility analyses, and to
separate the definition of access from the study of its effects. This
will in turn enhance the ability of planners to consider how multiple
attributes of a park --- from its location to its size to its amenities
and beyond --- benefit the health of the community the park serves.

\begin{acks}
This project was funded by the Speedwell Foundation. We are grateful to Rachel
Samuels and Neda Madi for helping to assemble the data.
\end{acks}

@@

\hypertarget{appendix}{%
\subsection{Supplementary Material}\label{appendix}}
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}

In this supplementary material we present the complete estimation results for the
models relating different definitions of access to physical activity (in
Table \ref{tab:pa-fullmodels}) and to obesity (in Table
\ref{tab:ob-fullmodels}). In each case we also present a base model with
no accessibility statistics for comparison.

@@

(Intercept)                         & $-24.5190^{*}$         & $-24.8266^{*}$         & $-24.8920^{*}$         & $-24.7176^{*}$         \\
                                    & $ [-41.5947; -7.4433]$ & $ [-41.7445; -7.9087]$ & $ [-41.8372; -7.9468]$ & $ [-41.7891; -7.6461]$ \\
log(Density)                        & $0.1740^{*}$           & $0.1766^{*}$           & $0.1757^{*}$           & $0.1686^{*}$           \\
                                    & $ [  0.0348;  0.3132]$ & $ [  0.0375;  0.3156]$ & $ [  0.0366;  0.3148]$ & $ [  0.0293;  0.3079]$ \\
log(Income)                         & $5.9786^{*}$           & $5.9976^{*}$           & $5.9964^{*}$           & $5.9767^{*}$           \\
                                    & $ [  5.5540;  6.4032]$ & $ [  5.5737;  6.4215]$ & $ [  5.5723;  6.4205]$ & $ [  5.5523;  6.4011]$ \\
Fulltime                            & $0.1283^{*}$           & $0.1275^{*}$           & $0.1275^{*}$           & $0.1285^{*}$           \\
                                    & $ [  0.1098;  0.1468]$ & $ [  0.1090;  0.1460]$ & $ [  0.1090;  0.1460]$ & $ [  0.1100;  0.1470]$ \\
College-educated                    & $0.0075$               & $0.0076$               & $0.0073$               & $0.0083$               \\
                                    & $ [ -0.0159;  0.0310]$ & $ [ -0.0158;  0.0309]$ & $ [ -0.0161;  0.0306]$ & $ [ -0.0152;  0.0317]$ \\
Single Adults                       & $-0.0363^{*}$          & $-0.0362^{*}$          & $-0.0360^{*}$          & $-0.0366^{*}$          \\
                                    & $ [ -0.0527; -0.0198]$ & $ [ -0.0526; -0.0198]$ & $ [ -0.0524; -0.0196]$ & $ [ -0.0530; -0.0201]$ \\
Youth (0-17)                        & $-0.1306^{*}$          & $-0.1311^{*}$          & $-0.1310^{*}$          & $-0.1311^{*}$          \\
                                    & $ [ -0.1572; -0.1040]$ & $ [ -0.1576; -0.1046]$ & $ [ -0.1576; -0.1045]$ & $ [ -0.1577; -0.1045]$ \\
Young adults (18-34)                & $0.0283^{*}$           & $0.0293^{*}$           & $0.0294^{*}$           & $0.0281^{*}$           \\
                                    & $ [  0.0081;  0.0484]$ & $ [  0.0092;  0.0495]$ & $ [  0.0092;  0.0495]$ & $ [  0.0079;  0.0482]$ \\
Seniors (65+)                       & $0.0430^{*}$           & $0.0403^{*}$           & $0.0408^{*}$           & $0.0427^{*}$           \\
                                    & $ [  0.0157;  0.0704]$ & $ [  0.0130;  0.0677]$ & $ [  0.0135;  0.0682]$ & $ [  0.0153;  0.0700]$ \\
Black population share              & $-0.0499^{*}$          & $-0.0499^{*}$          & $-0.0498^{*}$          & $-0.0497^{*}$          \\
                                    & $ [ -0.0587; -0.0412]$ & $ [ -0.0586; -0.0412]$ & $ [ -0.0585; -0.0411]$ & $ [ -0.0584; -0.0409]$ \\
Asian population share              & $-0.0772^{*}$          & $-0.0767^{*}$          & $-0.0768^{*}$          & $-0.0774^{*}$          \\
                                    & $ [ -0.0877; -0.0666]$ & $ [ -0.0873; -0.0662]$ & $ [ -0.0874; -0.0663]$ & $ [ -0.0879; -0.0669]$ \\
Hispanic population share           & $-0.1021^{*}$          & $-0.1025^{*}$          & $-0.1025^{*}$          & $-0.1020^{*}$          \\
                                    & $ [ -0.1112; -0.0929]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1111; -0.0928]$ \\
Other Minorities                    & $0.0006$               & $0.0035$               & $0.0037$               & $-0.0005$              \\
                                    & $ [ -0.0882;  0.0894]$ & $ [ -0.0851;  0.0921]$ & $ [ -0.0850;  0.0923]$ & $ [ -0.0893;  0.0883]$ \\
$\gamma$: log(Density)              & $1.1105^{*}$           & $1.0987^{*}$           & $1.1030^{*}$           & $1.0928^{*}$           \\
                                    & $ [  0.7245;  1.4964]$ & $ [  0.7156;  1.4817]$ & $ [  0.7196;  1.4865]$ & $ [  0.7063;  1.4793]$ \\
$\gamma$: log(Income)               & $1.9269^{*}$           & $1.9646^{*}$           & $1.9570^{*}$           & $1.9189^{*}$           \\
                                    & $ [  0.8913;  2.9625]$ & $ [  0.9370;  2.9922]$ & $ [  0.9282;  2.9857]$ & $ [  0.8836;  2.9541]$ \\
$\gamma$: Fulltime                  & $-0.0360$              & $-0.0396$              & $-0.0388$              & $-0.0363$              \\
                                    & $ [ -0.0835;  0.0115]$ & $ [ -0.0869;  0.0076]$ & $ [ -0.0861;  0.0085]$ & $ [ -0.0837;  0.0112]$ \\
$\gamma$: College-educated          & $-0.0707^{*}$          & $-0.0711^{*}$          & $-0.0721^{*}$          & $-0.0731^{*}$          \\
                                    & $ [ -0.1307; -0.0107]$ & $ [ -0.1306; -0.0116]$ & $ [ -0.1317; -0.0125]$ & $ [ -0.1332; -0.0131]$ \\
$\gamma$: Single Adults             & $-0.0081$              & $-0.0085$              & $-0.0077$              & $-0.0076$              \\
                                    & $ [ -0.0506;  0.0344]$ & $ [ -0.0507;  0.0336]$ & $ [ -0.0499;  0.0345]$ & $ [ -0.0501;  0.0348]$ \\

>>>>

In spite of its flexibility and basis in choice theory, utility-based
accessibility measures have not received much application in the park
accessibility literature compared with distance-based or even
gravity-based measures. \citet{Vale2016} present a descriptive
classification of active accessibility techniques, and explicitly
dismiss utility-based metrics for incorporating randomness. This is a
curious decision: The accessibility formula presented in Equation
\ref{eq:utility} is the expectation of a random utility process, but the
measure is not in and of itself random any more than the gravity model
is random. Utility-based accessibility metrics are commonly used,
however, in alternatives analyses of transit infrastructure improvements
\citep{DeJong2007}. A reason for this is likely that a regional travel
demand model is available to the analysts, thus making calibrated and
multimodal logsums readily available \citep{Geurs2010}.

To our knowledge, there has been no previous attempt to examine access
to parks in a metropolitan area using a utility-based definition as the
primary indicator of access. Consequently, there has also been no
previous effort to examine the effect of park access on health outcomes
using this theoretically attractive technique. In this study, we first
develop a utility-based measure of park access in New York City, and
then apply this measure to study the effect of access to public parks on
aggregate health outcomes.

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.318e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect to retain the null
hypothesis that the coefficients are equivalent, as the differences are
at no point practically different from each other. The consequences of
rejecting the null hypothesis in this case would be to suggest a model
with spatial dependence of the dependent variable; as stated above, we
feel that such a relationship is unreasonable. As a consequence of these
analyses, we adopt the SDEM specification moving forward as the spatial
lag of the errors is significant and the overall log likelihood of the
SDEM is higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Sep 24 13:27:59 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

\midrule
Log Likelihood & \multicolumn{3}{c}{$-4,815$} & & \multicolumn{3}{c}{$-4,433$}\\
Num.Obs.       & \multicolumn{3}{c}{$2,099$}   & & \multicolumn{3}{c}{$2,099$}\\
\bottomrule
\end{tabular}
\end{table*}

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and
accessibility coefficients for two models using different specifications
of the utility equation, as well as the ten-minute walk buffer
calculated by ParkScore. Note that the model called ``Size and
Distance'' is precisely the model labeled ``SDEM'' in Table
\ref{tab:slx-sdem}. The controlling covariates are suppressed for
clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels}
of the Supplementary Material. Each of the two utility-based
specifications is significant at the \(\alpha = 0.05\) level or lower,
and is of the hypothesized direction That is, residents living in tracts
with increased utility-based accessibility to green spaces show a
significantly higher physical activity participation rate. Taking the
rough mean of the two estimated utility-based coefficients, moving from
the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
(\(A_i = 3\)) is expected to raise the physical activity rate by 1.32
percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor
park access is anywhere between 0.3 and 2.1 percentage points.

In contrast, 10-minute walk buffer is considerably less useful at
isolating the effects of park ``access'' on physical activity rates. As
so few tracts are located outside of the buffer, the standard error of
the estimated effect is large and implies an effect on activity rates
anywhere from a loss of 0.18 percentage points to a gain of 1.35.

@@

This paper applies a previously presented but seldom applied
accessibility statistic that could, in theory, accommodate many
attributes of the destination parks as well as the people who might use
them. As an illustration: the park-going population could be separated
into at least four delineated clusters, each preferring different
amenities of a park:

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. The set of amenities we included in the
utility calculation --- and the contribution of each amenity to the
overall utility --- was dictated by the availability of open data on the
park amenities in New York City and our ability to find comparable prior
studies with transferable utility parameters. It is remarkable that our
two utility specifications --- one with size and distance, and one with
size and distance plus amenities --- result in such similar model
estimates. This may indicate that the utility is driven largely by size
and distance, or that the additional park amenities we included in the
utility specification are spatially distributed in a way that correlates
with the health outcomes. Either way, further analysis examining more
amenity variables is warranted. We can envision a study where mobile
device data revealing the home locations of park users would be paired
with more detailed park amenities and use data (e.g.~geolocated Twitter
data \emph{a la} \citet{roberts2017using}) to estimate the utility
contribution of these features. This could in turn provide a more
nuanced understanding of the relationship between park accessibility,
use, and health outcomes.

@@

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted. We acknowledge that a utility-based framework
for access may be more technically difficult for some practitioners to
independently construct for their analyses than an isochrone or even a
gravity-based measure. That said, it may not be necessary for practicing
planners to construct this measure themselves: web-based tools such as
ParkIndex \citep{Kaczynski2016} and even WalkScore
(\url{https://www.walkscore.com}) abstract complex methodologies into
tools that planners can and do readily apply.

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park access and public, previous literature has
produced mixed findings, perhaps owing to the wide range of
accessibility definitions. Using New York City as a case study, we
presented a holistic and flexible measurement for park accessibility
that compares the continuous distance to all parks in the region,
weighted against the size of the park and its other amenities, with
weights determinable through revealed preferences. In terms of physical
activity, we found a positive relationship where the least
park-accessible tracts have an expected physical activity participation
rate between 0.06 and 1.8 percentage points lower than the most
accessible tracts. We also found a suggestive though not significant
relationship between park accessibility and expected obesity rates
\emph{in addition to} the effect of physical activity participation.

In both cases a common, isochrone-based analysis estimated a
statistically weak relationship with greater uncertainty. Isochrone
analyses are relatively common in the literature, perhaps because of the
widespread availability of and training in GIS software. In spite of
their widespread use, isochrones are relatively limited in terms of both
their theoretical underpinnings and their flexibility to accommodate
attributes of parks beyond their proximity. And even proximity may not
be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends a
more comprehensive and flexible approach for measuring the impact of
park access on health outcomes.

Adopting utility-based accessibilities of the kind used in this study
will allow researchers to encompass the full range of park amenities in
their accessibility analyses, and to separate the definition of access
from the study of its effects. This will in turn enhance the ability of
planners to consider how multiple attributes of a park --- from its
location to its size to its amenities and beyond --- benefit the health
of the community the park serves.

\begin{acks}
This project was funded by the Speedwell Foundation. We are grateful to Rachel
Samuels and Neda Madi for helping to assemble the data. We are also grateful for
the three anonymous reviewers, whose comments significantly strengthened the 
manuscript.
\end{acks}

@@

\hypertarget{appendix}{%
\subsection{Appendix}\label{appendix}}

In this appendix we present the complete estimation results for the
models relating different definitions of access to physical activity (in
Table \ref{tab:pa-fullmodels}) and to obesity (in Table
\ref{tab:ob-fullmodels}). In each case we also present a base model with
no accessibility statistics for comparison.

@@

(Intercept)                         & $-24.5190^{*}$         & $-24.7352^{*}$         & $-24.8758^{*}$         & $-24.7176^{*}$         \\
                                    & $ [-41.5947; -7.4433]$ & $ [-41.5391; -7.9312]$ & $ [-41.7511; -8.0005]$ & $ [-41.7891; -7.6461]$ \\
log(Density)                        & $0.1740^{*}$           & $0.1760^{*}$           & $0.1753^{*}$           & $0.1686^{*}$           \\
                                    & $ [  0.0348;  0.3132]$ & $ [  0.0371;  0.3150]$ & $ [  0.0362;  0.3143]$ & $ [  0.0293;  0.3079]$ \\
log(Income)                         & $5.9786^{*}$           & $6.0134^{*}$           & $6.0060^{*}$           & $5.9767^{*}$           \\
                                    & $ [  5.5540;  6.4032]$ & $ [  5.5901;  6.4368]$ & $ [  5.5822;  6.4298]$ & $ [  5.5523;  6.4011]$ \\
Fulltime                            & $0.1283^{*}$           & $0.1271^{*}$           & $0.1272^{*}$           & $0.1285^{*}$           \\
                                    & $ [  0.1098;  0.1468]$ & $ [  0.1086;  0.1455]$ & $ [  0.1087;  0.1457]$ & $ [  0.1100;  0.1470]$ \\
College-educated                    & $0.0075$               & $0.0077$               & $0.0071$               & $0.0083$               \\
                                    & $ [ -0.0159;  0.0310]$ & $ [ -0.0156;  0.0310]$ & $ [ -0.0162;  0.0305]$ & $ [ -0.0152;  0.0317]$ \\
Single Adults                       & $-0.0363^{*}$          & $-0.0365^{*}$          & $-0.0362^{*}$          & $-0.0366^{*}$          \\
                                    & $ [ -0.0527; -0.0198]$ & $ [ -0.0528; -0.0201]$ & $ [ -0.0526; -0.0198]$ & $ [ -0.0530; -0.0201]$ \\
Youth (0-17)                        & $-0.1306^{*}$          & $-0.1320^{*}$          & $-0.1316^{*}$          & $-0.1311^{*}$          \\
                                    & $ [ -0.1572; -0.1040]$ & $ [ -0.1585; -0.1055]$ & $ [ -0.1581; -0.1050]$ & $ [ -0.1577; -0.1045]$ \\
Young adults (18-34)                & $0.0283^{*}$           & $0.0292^{*}$           & $0.0293^{*}$           & $0.0281^{*}$           \\
                                    & $ [  0.0081;  0.0484]$ & $ [  0.0092;  0.0493]$ & $ [  0.0092;  0.0494]$ & $ [  0.0079;  0.0482]$ \\
Seniors (65+)                       & $0.0430^{*}$           & $0.0386^{*}$           & $0.0398^{*}$           & $0.0427^{*}$           \\
                                    & $ [  0.0157;  0.0704]$ & $ [  0.0112;  0.0659]$ & $ [  0.0125;  0.0671]$ & $ [  0.0153;  0.0700]$ \\
Black population share              & $-0.0499^{*}$          & $-0.0499^{*}$          & $-0.0497^{*}$          & $-0.0497^{*}$          \\
                                    & $ [ -0.0587; -0.0412]$ & $ [ -0.0586; -0.0412]$ & $ [ -0.0585; -0.0410]$ & $ [ -0.0584; -0.0409]$ \\
Asian population share              & $-0.0772^{*}$          & $-0.0764^{*}$          & $-0.0766^{*}$          & $-0.0774^{*}$          \\
                                    & $ [ -0.0877; -0.0666]$ & $ [ -0.0870; -0.0659]$ & $ [ -0.0872; -0.0661]$ & $ [ -0.0879; -0.0669]$ \\
Hispanic population share           & $-0.1021^{*}$          & $-0.1023^{*}$          & $-0.1024^{*}$          & $-0.1020^{*}$          \\
                                    & $ [ -0.1112; -0.0929]$ & $ [ -0.1114; -0.0932]$ & $ [ -0.1115; -0.0933]$ & $ [ -0.1111; -0.0928]$ \\
Other Minorities                    & $0.0006$               & $0.0047$               & $0.0043$               & $-0.0005$              \\
                                    & $ [ -0.0882;  0.0894]$ & $ [ -0.0837;  0.0931]$ & $ [ -0.0842;  0.0929]$ & $ [ -0.0893;  0.0883]$ \\
$\gamma$: log(Density)              & $1.1105^{*}$           & $1.0873^{*}$           & $1.0967^{*}$           & $1.0928^{*}$           \\
                                    & $ [  0.7245;  1.4964]$ & $ [  0.7062;  1.4684]$ & $ [  0.7145;  1.4789]$ & $ [  0.7063;  1.4793]$ \\
$\gamma$: log(Income)               & $1.9269^{*}$           & $1.9780^{*}$           & $1.9650^{*}$           & $1.9189^{*}$           \\
                                    & $ [  0.8913;  2.9625]$ & $ [  0.9563;  2.9997]$ & $ [  0.9397;  2.9902]$ & $ [  0.8836;  2.9541]$ \\
$\gamma$: Fulltime                  & $-0.0360$              & $-0.0411$              & $-0.0394$              & $-0.0363$              \\
                                    & $ [ -0.0835;  0.0115]$ & $ [ -0.0882;  0.0059]$ & $ [ -0.0865;  0.0078]$ & $ [ -0.0837;  0.0112]$ \\
$\gamma$: College-educated          & $-0.0707^{*}$          & $-0.0704^{*}$          & $-0.0718^{*}$          & $-0.0731^{*}$          \\
                                    & $ [ -0.1307; -0.0107]$ & $ [ -0.1296; -0.0112]$ & $ [ -0.1312; -0.0125]$ & $ [ -0.1332; -0.0131]$ \\
$\gamma$: Single Adults             & $-0.0081$              & $-0.0094$              & $-0.0080$              & $-0.0076$              \\
                                    & $ [ -0.0506;  0.0344]$ & $ [ -0.0514;  0.0325]$ & $ [ -0.0501;  0.0341]$ & $ [ -0.0501;  0.0348]$ \\
$\gamma$: Youth (0-17)              & $-0.0111$              & $-0.0128$              & $-0.0108$              & $-0.0120$              \\
